---
title: "Features Extraction"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(zoo)
```

# Code for feature extraction

1. Set sliding widow parameters
2. Calculate features for particular user  
2. Repeat steps 1- 3 for all files (#1-10)  
3. Combine features from different users in final tibble  
4. Make csv file with features  

4. Repeat steps 1- 3 for all files (#1-10)  
5. Combine features from different users in final tibble  
6. Make csv file with features  
  
# 1. Settings

## 1.1 Sliding window parameters
   
The raw data is divided into identification intervals of 100 samples width with 50% overlap:  
Sampling freaquency: $f_s = 52 Hz$;  
Number of samples (sliding window length) $N = 100$;  
Length of data frame: $L = N \over f_s$ (2 sec max!)
```{r}
sample_Hz <- 52
sample_N <- 100 
overlap <- 0.5
length_DF <- round(sample_N / sample_Hz)
```

## 1.2 Parameters for peak detection:
```{r}
peak.detection.window <- 3 # w
peak.detection.span <- 0.1 # span
```

### 2.1 Mean  
1) raw_mean_ax;  
2) raw_mean_ay;  
3) raw_mean_az;
4) fft_mean_ax;  
5) fft_mean_ay;  
6) fft_mean_az;  

  

