---
title: "Features Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

library(tidyverse)
library(caret)
```

# Load features:

```{r}
raw_features <- readRDS("data/preprocessing/features_v1.rds")
```

# Data normalization

```{r}
as.character(1:10) %>% 
  map_dfr(~filter(df, user_id == .) %>% 
            scale %>%
            as_tibble %>% 
            mutate(user_id = rep(.x, each = nrow(.))) %>% 
            select(user_id, everything()))
```


## TEST data
```{r}
as.character(1:10) %>% 
  map_dfr(~filter(raw_features, user_id == .) %>% 
            slice(30:34)) -> test.raw.features
test.raw.features
```
Normalize for single user:
```{r}
test.raw.features %>% 
  filter(user_id == 1) %>% 
  select(-user_id) -> user1
user1
```
Test norm
```{r}
test_norm_vec <- pull(user1, 2)
test_norm_vec %>% 
  map_dbl(~(.x - mean(test_norm_vec)) / sd(test_norm_vec)) -> test.res
test.res
```
Use scale
```{r}
scale(test_norm_vec)
```
Use scale for tibble:
```{r}
a3 <- scale(user1[,1:3])
a3
```
Test normalization for multiple users:
```{r}
as.character(1:10) %>% 
  map_dfr(~filter(test.raw.features, user_id == .) %>% 
            select(-user_id) %>% 
            scale %>%
            as_tibble %>% 
            mutate(user_id = rep(.x, each = nrow(.))) %>% 
            select(user_id, everything()))
```

## Do normalization
```{r}
as.character(1:10) %>% 
  map_dfr(~filter(raw_features, user_id == .) %>% 
            select(-user_id) %>% 
            scale %>%
            as_tibble %>% 
            mutate(user_id = rep(.x, each = nrow(.))) %>% 
            select(user_id, everything())) -> norm.features
norm.features
```
Save data:
```{r}
saveRDS(norm.features, "data/preprocessing/norm_features_v1.rds")
```

# Features selecting

## Perform PCA

```{r}
pc <- prcomp(raw_features[ ,-1], scale = T)
pc %>% summary()
```
## Compute correlation matrix

### Raw features
```{r}
corrmat <- cor(raw_features[,-1])
corrmat
```
Highcorr contains the first elements of all pairs of highly correlated features
```{r}
findCorrelation(corrmat, cutoff = 0.7, names = T, exact = T)
```

### Normalized features 

```{r}
corrmat.norm <- cor(norm.features[,-1])
```
Highcorr contains the first elements of all pairs of highly correlated features
```{r}
findCorrelation(corrmat.norm, cutoff = 0.7, names = T, exact = T)
```
