---
title: "Features Extraction"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

library(tidyverse)
library(zoo)

source("../auxiliary_functions.R")
```

# 1. Settings

## 1.1 Sliding window parameters
   
The raw data is divided into identification intervals of 100 samples width with 50% overlap:  
Sampling freaquency: $f_s = 52 Hz$;  
Number of samples (sliding window length) $N = 100$;  
Length of data frame: $L = N \over f_s$ (2 sec max!)
```{r}
sample_Hz <- 52
sample_N <- 100 
overlap <- 0.5
length_DF <- round(sample_N / sample_Hz)
```

## 1.2 Parameters for peak detection:
```{r}
peak.detection.window <- 3 # w
peak.detection.span <- 0.1 # span
```

## 2. Here is a list of features

Add features description!!! 

## 3. Load data
```{r}
df <- readRDS("pre_features_activity1.rds")
```

### **VERY EXPENSIVE OPERATION!!!**

## 4. Extract features for users from 1 to 10: 

```{r}
users.id.list <- as.character(1:10)

users.id.list %>% 
  map_dfr(~filter(df, user_id == .) %>% 
            features.extract() %>% 
            mutate(user_id = rep(.x, each = nrow(.))) %>% 
            select(user_id, everything())) -> features
features
```

## 5. Save features to .rds file:

```{r}
saveRDS(features, "features_activity1_v1.rds")
```
