---
title: "Data exploration"
output: slidy_presentation 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(zoo)
```


```{r}
data4features <- readRDS("../data/preprocessing/pre_features_activity4.rds")
```
Choose user 1 data:
```{r}
user1 <- filter(data4features, user_id == 1)
```

# 1. Set sliding window parameters
   
The raw data is divided into identification intervals of 100 samples width with 50% overlap:  
Sampling freaquency: $f_s = 52 Hz$;  
Number of samples (sliding window length) $N = 100$;  
Length of data frame: $L = N / f_s$ (2 sec max!)
```{r}
sample_Hz <- 52
sample_N <- 100 
overlap <- 0.5
length_DF <- round(sample_N / sample_Hz)
```

# 2. Fast Fourier Transformation 

Build spectrogramma on raw data 
```{r}
user1x.spec <- spectrum(user1$ax, log = "no", span = 10, plot = FALSE, detrend = T, demean = F)
spu1_x <- user1x.spec$freq * sample_Hz
spu1_y <- 2*user1x.spec$spec
plot(spu1_y ~ spu1_x, xlab = "frequency", ylab = "spectral density", type = "l", xlim = c(0, 10))
```

Let's make detrending signal by using diff() as suggest [here](https://stackoverflow.com/questions/14010605/fast-fourier-transform-in-r?rq=1)
```{r}
user1x.spec <- spectrum(diff(user1$ax), log = "no", span = 50, plot = FALSE, detrend = T, demean = T)
spu1_x <- user1x.spec$freq * sample_Hz
spu1_y <- 2*user1x.spec$spec
plot(spu1_y ~ spu1_x, xlab = "frequency", ylab = "spectral density", type = "l", xlim = c(0, 12))
```

# 3. Peak detection

Do some investigation
```{r}
df_peak <- user1[1:100,]
ggplot(df_peak, aes(x = id, y = ax)) +
  geom_line(color = "red")
```

I've found this post here  
[Data Smoothing and Peak Detection](https://rpubs.com/mengxu/peak_detection)
```{r}
x <- df_peak$id
y <- df_peak$ax

argmax <- function(x, y, w=1, ...) {
  #require(zoo)
  n <- length(y)
  y.smooth <- loess(y ~ x, ...)$fitted
  y.max <- rollapply(zoo(y.smooth), 2*w+1, max, align="center")
  delta <- y.max - y.smooth[-c(1:w, n+1-1:w)]
  i.max <- which(delta <= 0) + w
  list(x=x[i.max], i=i.max, y.hat=y.smooth)
}

test.find.peak <- function(w, span) {
  peaks <- argmax(x, y, w=w, span=span)

  plot(x, y, cex=0.75, col="Gray", main=paste("w = ", w, ", span = ", span, sep=""))
  lines(x, peaks$y.hat,  lwd=2) #$
  y.min <- min(y)
  sapply(peaks$i, function(i) lines(c(x[i],x[i]), c(y.min, peaks$y.hat[i]), col="Red", lty=2))
  points(x[peaks$i], peaks$y.hat[peaks$i], col="Red", pch=19, cex=1.25)
}
```

View plot:
```{r}
test.find.peak(4, 0.05)
```

Change some parameters
```{r}
test.find.peak(3, 0.1)
```

