---
title: "Data cleaning and trasformation for features extraction"
output: slidy_presentation 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, fig.width = 9)

library(tidyverse)
source("../auxiliary_functions.R")
```

# 1.Create features 

Chose activity type
```{r}
activity <- 4
```

# 1.1 Read files  

List of files:
```{r}
(all_files <- list.files("../data/raw", pattern = "*.csv", full.names = T))
```

Get list of necessary files (1 to 10):
```{r}
(my_files <- grep(paste0("\\b", "(\\d|\\d0)", "\\b"), all_files, value = TRUE))
```

## 1.2 Make common dataset from chosen files  
First test ...
```{r}
grep("\\b[137]\\b", all_files, value = TRUE) %>% 
  map_dfr( ~ transform_data(df = read.csv(.),
                            user_id = str_extract(., "\\d+"),
                            activ_id = activity, start_id = 1, end_id = nrow(.))) %>%
  count(user_id)
```

### 3.1 Choose accectable data range

**We need to choose range of "good" data for all user_id. For this let's build plots to visual estimation of data.**  
Make dataset from  10 files for EDA:
```{r}
eda_df <- grep("\\b(\\d|\\d0)\\b", all_files, value = TRUE) %>% 
  map_dfr( ~ transform_data(df = read.csv(.),
                            user_id = str_extract(., "\\d+"),
                            activ_id = activity, start_id = 1, end_id = nrow(.)))
eda_df
```
Make plots to see raw data by three axis. Full range:
```{r}
eda_df %>% 
  ggplot() + 
    geom_line(aes(x = id, y = ax), color = "black") +
    geom_line(aes(x = id, y = ay), color = "red") +
    geom_line(aes(x = id, y = az), color = "green") +
    facet_wrap(user_id ~ ., scales = "free", ncol = 2)
```
Data range by users:
```{r}
count(eda_df, user_id)
```

Overview left data range:
```{r}
eda_df %>% 
  ggplot() + 
    geom_line(aes(x = id, y = ax), color = "black") +
    geom_line(aes(x = id, y = ay), color = "red") +
    geom_line(aes(x = id, y = az), color = "green") +
    geom_vline(xintercept = 4000) +
    coord_cartesian(xlim = c(0, 5000)) +
    facet_wrap(user_id ~ ., scales = "free", ncol = 2)
```
  
... and right data range:
```{r}
eda_df %>% 
  ggplot() + 
    geom_line(aes(x = id, y = ax), color = "black") +
    geom_line(aes(x = id, y = ay), color = "red") +
    geom_line(aes(x = id, y = az), color = "green") +
    geom_vline(xintercept = 20800) +
    coord_cartesian(xlim = c(20000, 25000)) +
    facet_wrap(user_id ~ ., scales = "free", ncol = 2)
```

Chose acceptable range:
```{r, cache=TRUE}
eda_df %>% 
  ggplot() + 
    geom_line(aes(x = id, y = ax), color = "black") +
    geom_line(aes(x = id, y = ay), color = "red") +
    geom_line(aes(x = id, y = az), color = "green") +
    geom_vline(xintercept = c(4000, 20800)) +
    coord_cartesian(xlim = c(4000, 20800)) +
    facet_wrap(user_id ~ ., scales = "free", ncol = 2)
```

**So, chosen range:**
```{r}
chosen.left.border <- 4000
chosen.right.border <- 20800
```

### 3.2 Recalculate final dataset based on acceptable data range

Make dataset
```{r, cache=TRUE}
pre_features_df <- grep("\\b(\\d|\\d0)\\b", all_files, value = TRUE) %>% 
  map_dfr( ~ transform_data(df = read.csv(.),
                            user_id = str_extract(., "\\d+"),
                            activ_id = activity,
                            start_id = chosen.left.border,
                            end_id = chosen.right.border)) %>% 
  select(-activity)
pre_features_df
```
Build plot:
```{r}
pre_features_df %>% 
  ggplot() + 
    geom_line(aes(x = id, y = ax), color = "black") +
    geom_line(aes(x = id, y = ay), color = "red") +
    geom_line(aes(x = id, y = az), color = "green") +
    facet_wrap(user_id ~ ., scales = "free", ncol = 2)
```
Save data into file  
```{r, eval=FALSE}
#saveRDS(pre_features_df, paste0("pre_features_activity", activity, ".rds"))
```

